Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-27 Grassmannian_cells.tex
Section 3.2 edits, Corollary 3.43 is next

Recall that, given $\CC$-representations $X$ and $Y$ of $Q$, any tuple of linear maps $(g_\alpha:X_{s(\alpha)}\to Y_{t(\alpha)})_{\alpha\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term given by the vector spaces $Z_i=X_i\oplus Y_i$ for $i\in Q_0$ and the linear maps $Z_\alpha=\begin{pmatrix} X_\alpha & 0 \\ g_\alpha & Y_\alpha \end{pmatrix}$ for $\alpha\in Q_1$. 
In general, considering the linear map  
\begin{align}\label{eq:homext}d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_\CC(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_\CC(X_{s(\alpha)},Y_{t(\alpha)}),\qquad (f_i)_{i\in Q_0}\mapsto(f_{t(\alpha)}\circ X_\alpha-Y_\alpha\circ f_{s(\alpha)})_{\alpha\in Q_1},\end{align}
we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.

@@

Fix a natural number $n\geq 3$ and write $W_n:=W_{K(n)}$ for the free group generated by the arrows $\alpha_i$, $1\le i\le n$, of $K(n)$.
In this section, we fix compatible bases for each $H_m:=\Hom(P_m,P_{m+1})$ and use these to lift the (truncated) preprojective representations of the quiver $K(n)$ to the universal cover~$\widetilde{K(n)}$.
This lifting will rigidify the situation, allowing more precise control over these representations and their subrepresentation structure.
Of particular importance is Corollary~\ref{cor:perpendicular} which has no reasonable analogue for $K(n)$.
One main advantage of the lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering quiver $\widetilde{K(n)}$.

@@

To construct the lifts, first recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying the iterated reflection $\tilde\Sigma_i:=\prod_{w\in W_n}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
Moreover, under this operation all sinks of~$\widetilde{K(n)}$ become sources and vice versa.
The preprojective lifts we use are defined by the following analogue of the recursions of Remark~\ref{rem:reflection recursion}.
\begin{itemize}
  \item For $m=1$, we consider the lift $\tilde P_1$ satisfying $\dim(\tilde P_1)_{(1,1)}=1$ and $\dim (\tilde P_1)_{(i,w)}=0$ for $(i,w)\neq (1,1)$.
  \item For $m=2$, we consider the lift $\tilde P_2$ satisfying $\dim (\tilde P_2)_{(2,1)}=\dim (\tilde P_2)_{(1,\alpha_i)}=1$ for $1\le i\le n$ and $\dim(\tilde P_2)_{(i,w)}=0$ for $(i,w)\notin\{(2,1),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
  \item For $m\geq 3$, we build the lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates.
    More precisely, we set
    \begin{align}
      \label{eq:recursive covers}
      \tilde P_m:=(\tilde\Sigma_2 \tilde P_{m-1})^{\sigma}\qquad\text{or}\qquad\tilde P_{m+1}:=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1},
    \end{align}
    where $(-)^\sigma:\rep\widetilde{K(n)}^{op}\to\rep\widetilde{K(n)}$ is the lift of the corresponding functor for $K(n)$.
\end{itemize}

It will be rather important that our chosen lifts of $\tilde P_{2l}$ and $\tilde P_{2l-1}$, $l\ge1$, live on two different components of the universal covering quiver.
Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e.~$w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation~$\tilde P_m$ by the action of $w\in W_n$.
To simplify the notation, we abbreviate $\tilde P_{2l-1,i}:=\tilde P_{2l-1,\alpha_i}$ and $\tilde P_{2l,i}:=\tilde P_{2l,\alpha_i^{-1}}$.
\begin{lemma}
  For each $m\ge1$, the representation $\tilde P_{m+1}$ has precisely $n$ subrepresentations covering $P_m$.
  These are the representations $\tilde P_{m,i}$ corresponding to the $n$ different arrows of $K(n)$. 
\end{lemma}
\begin{proof}
  This is clear for $m=1$ and follows in general by applying the identities \eqref{eq:recursive covers}.
\end{proof}
\begin{remark}
  Note that the dimension vectors of the lifted preprojectives $\tilde P_m$ are symmetric under permutations of the arrows of $K(n)$ (or rather the corresponding operation on $\widetilde{K(n)}$).
  In particular, they all have the same middle vertex $(1,1)$ if $m$ is odd and middle vertex $(2,1)$ if $m$ is even.
\end{remark}

The next result establishes some basic homological properties of these translated preprojective representations.
\begin{lemma}
  \label{le:homdecomposition}
  For $m\geq 1$, the following hold.
  \begin{enumerate}
    \item We have $\Hom(P_m,P_{m+1})\cong\bigoplus\limits_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
    \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
    \item For $j\in\{1,\ldots,n\}$, we have
      \[\Hom(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m,j},\tilde P_{m+1})=0.\]
    \item For each proper subset $I\subsetneq\{1,\ldots,n\}$, there exists a truncated preprojective representation~$\tilde P_{m+1}^I$ fitting into an exact sequence 
      \begin{equation}
        \label{ses1}
        \ses{\bigoplus_{i\in I} \tilde P_{m,i}}{\tilde P_{m+1}}{\tilde P_{m+1}^I}.
      \end{equation}
      Moreover, $G(\tilde P_{m+1}^I)$ is a truncated preprojective of $K(n)$ for each $I\subsetneq\{1,\ldots,n\}$.
  \end{enumerate}
\end{lemma}
\begin{remark}
  Note that when $I=\varnothing$, it follows from the definition that $\tilde P_{m+1}^I=\tilde P_{m+1}$.
\end{remark}
\begin{proof}
  Part (1) is immediate from Theorem~\ref{covering}.
  Part (2) is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq j\leq n$, we have 
  $$\CC=\Hom(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m,j}).$$
  But $\Hom(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.

@@

  For part (4), observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to the subspace $V\subset H_m$ spanned by the generators of the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
  The map $\bigoplus_{i\in I} \tilde P_{m,i}\to\tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^I$ and the preceding discussion shows that $G(\tilde P_{m+1}^I)\cong P_{m+1}^V$ is truncated preprojective as well.
\end{proof}
In the following, we make use of this lemma and fix a basis of $\Hom(P_m,P_{m+1})$ which is compatible with the direct sum decomposition from part (1).
\begin{lemma}
  \label{le:properties}
  For $m\geq1$ and $I\subsetneq\{1,\ldots,n\}$, the following hold.
  \begin{enumerate}
    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\ne0$ if and only if $j\notin I$, in which case 
      \[\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Hom(\tilde P_{m,j},\tilde P_{m+1})=\CC.\] 
    \item We have $\Hom(\tilde P_{m+1},\tilde P_{m+1}^I)=\CC$ and $\Ext(\tilde P_{m+1},\tilde P_{m+1}^I)=0$. 
    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$.
      Also, $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ne0$ if and only if $j\in I$, in which case  
      \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Hom(\tilde P_{m,j},\tilde P_{m,j})=\CC.\] 
    \item We have $\Hom(P_{m+1}^I,P_{m+1}^I)=\CC$ and $\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0$.
      In particular, $P_{m+1}^I$ is an exceptional representation of $\widetilde{K(n)}$.
    %\item We have $\Hom(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=0$ and $\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\CC$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  Applying $\Hom(\tilde P_{m,j},-)$ to the sequence \eqref{ses1} gives the exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(\tilde P_{m,j},\bigoplus_{i\in I} \tilde P_{m,i}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}^I) \ar[r] & 0},\]
  where the final zero follows from Lemma~\ref{le:homdecomposition}.(2).
  Now the middle space is one-dimensional while the left-hand space vanishes if and only if $j\notin I$, this proves part (1).

@@

Now we introduce notation for locating lifted preprojectives as subrepresentations of other lifted preprojective representations.
Since we work only on two fixed components of $\widetilde{K(n)}$, the following notation will be useful in describing paths in these components.
For $l\ge1$, set
\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\}, i_j\ne i_{j+1}\text{ for $1\le j<l$}\}.\]
Depending on context (in particular, the parity of $m+1$ below), we will sometimes identify the word~$(i_1,\ldots,i_l)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_l}^{(-1)^{l+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_l}^{(-1)^l}\in W_n$.
In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$, we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
More precisely, we obtain a sequence of preprojective representations which uniquely determines the desired inclusion:
\[\tilde P_{m+1-k,\ui}\subset \tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-1,(i_1,i_2)}\subset \tilde P_{m,i_1}\subset\tilde P_{m+1}.\]

Consider a nonempty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$.
For $m\ge3$, define the representation 
\begin{lemma}
  Consider a nonempty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$. 
  For $m\ge2$, we have $\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)=\CC$.
  Moreover, the kernel of the unique morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is the following representation 
  \[\tilde P_m(I,j):=
    \begin{cases}
      \bigoplus_{\substack{1\leq i\leq n\\i\neq j}}\tilde P_{m-1,(j,i)}\oplus \bigoplus_{i\in I, i\ne j}\tilde P_{m-2,i} & \text{ if $m\geq 3$;}\\
      \bigoplus_{\substack{1\leq i\leq n\\i\neq j}}\tilde P_{1,(j,i)} & \text{ if $m=2$.}
    \end{cases}\]
\end{lemma}
\begin{proof}
  The first claim follows from Lemma~\ref{le:properties}.(3) by applying the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass}.
  Indeed, this gives the isomorphism
  \[\dim\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})=\CC.\]

  We establish the final claim directly for $m=2,3$ and then deduce the general case by applying the reflection recursions \eqref{eq:recursive covers}.
\end{proof}
%Note that by Lemma~\ref{le:properties}.(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $I\subsetneq J\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
%\[\ses{\bigoplus_{i\in J\setminus I}\tilde P_{m,i}}{\tilde P_m^I}{\tilde P_{m+1}^J}.\]

>>>>

Recall that, given $\CC$-representations $X$ and $Y$ of $Q$, any tuple of linear maps $(g_\alpha:X_{s(\alpha)}\to Y_{t(\alpha)})_{\alpha\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term given by the vector spaces $Z_i=X_i\oplus Y_i$ for $i\in Q_0$ and the linear maps $Z_\alpha=\begin{pmatrix} X_\alpha & 0 \\ g_\alpha & Y_\alpha \end{pmatrix}$ for $\alpha\in Q_1$. 
In general, considering the linear map  
\begin{align}
  \label{eq:homext}
  d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_\CC(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_\CC(X_{s(\alpha)},Y_{t(\alpha)}),
  \quad (f_i)_{i\in Q_0}\mapsto(f_{t(\alpha)}\circ X_\alpha-Y_\alpha\circ f_{s(\alpha)})_{\alpha\in Q_1},
\end{align}
we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.

@@

Fix a natural number $n\geq 3$.
Write $W_n:=W_{K(n)}$ for the free group generated by the arrows $\alpha_i$, $1\le i\le n$, of $K(n)$ and denote by $e\in W_n$ its identity element.
In this section, we fix compatible bases for each $H_m:=\Hom(P_m,P_{m+1})$ and use these to lift the (truncated) preprojective representations of the quiver $K(n)$ to the universal cover~$\widetilde{K(n)}$.
This lifting will rigidify the situation, allowing more precise control over these representations and their subrepresentation structure.
Of particular importance is Corollary~\ref{cor:perpendicular} which has no reasonable analogue for $K(n)$.
One main advantage of the lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering quiver $\widetilde{K(n)}$.

@@

To construct the lifts, first recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying the iterated reflection $\tilde\Sigma_i:=\prod_{w\in W_n}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
Moreover, under this operation all sinks of~$\widetilde{K(n)}$ become sources and vice versa.
The preprojective lifts we use are defined by the following analogue of the recursions of Remark~\ref{rem:reflection recursion}.
\begin{itemize}
  \item We consider the lift $\tilde P_1$ satisfying $\dim(\tilde P_1)_{(1,e)}=1$ and $\dim (\tilde P_1)_{(i,w)}=0$ for $(i,w)\neq (1,e)$.
  \item We consider the lift $\tilde P_2$ satisfying $\dim (\tilde P_2)_{(2,e)}=\dim (\tilde P_2)_{(1,\alpha_i)}=1$ for $1\le i\le n$ and $\dim(\tilde P_2)_{(i,w)}=0$ for $(i,w)\notin\{(2,e),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
  \item For $m\geq 3$, we build the lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates.
    More precisely, we set
    \begin{align}
      \label{eq:recursive covers}
      \tilde P_m:=\tilde\Sigma_2(\tilde P_{m-1})^{\sigma}\qquad\text{or}\qquad\tilde P_{m+1}:=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1},
    \end{align}
    where $(-)^\sigma:\rep\widetilde{K(n)}^{op}\to\rep\widetilde{K(n)}$ is the lift of the corresponding functor for $K(n)$.
\end{itemize}

It will be rather important that our chosen lifts of $P_{2l}$ for $l\ge1$ and our chosen lifts of $P_{2l-1}$ for $l\ge1$ live on two different components of the universal covering quiver.
Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e.~$w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation~$\tilde P_m$ by the action of $w\in W_n$.
To simplify the notation, we abbreviate $\tilde P_{2l-1,i}:=\tilde P_{2l-1,\alpha_i}$ and $\tilde P_{2l,i}:=\tilde P_{2l,\alpha_i^{-1}}$.
\begin{lemma}
  \label{le:shifted subreps}
  For each $m\ge1$, the representation $\tilde P_{m+1}$ has precisely $n$ subrepresentations covering $P_m$.
  These are the representations $\tilde P_{m,i}$ corresponding to the $n$ different arrows of $K(n)$. 
\end{lemma}
\begin{proof}
  This is clear for $m=1$ and follows in general by applying the identities \eqref{eq:recursive covers}.
\end{proof}
\begin{remark}
  Note that the dimension vectors of the lifted preprojectives $\tilde P_m$ are symmetric under permutations of the arrows of $K(n)$ (or rather the corresponding operation on $\widetilde{K(n)}$).
  In particular, they all have the same central vertex $(1,e)$ if $m$ is odd and central vertex $(2,e)$ if $m$ is even.
\end{remark}

\begin{example}
  \label{ex:lifted preprojectives}
  Here we explicitly describe the preprojective lifts $\tilde P_m$ for $m=2,3,4$ as well as their shifted preprojective subrepresentations as in Lemma~\ref{le:shifted subreps}.
  By Lemma~\ref{le:lifts of transjectives}, the lifts of all preprojectives are exceptional as representations of $\widetilde{K(n)}$ and thus they are uniquely determined by their dimension vectors.
  We make use of this fact below, stating only the support of the representation (also specifying those dimensions which are not one) and do not state the particular maps present in the lifts.
  We call this the \emph{support quiver} of the representation and let $W_n$ act on these quivers by translating all vertices.

  The representation $\tilde P_2$ is defined by the following quiver:
  \begin{equation}
    \label{dia:P2 quiver}
    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_n}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_n)}
  \end{equation}
  Then $\tilde P_{1,i}\subset\tilde P_2$ corresponds to the one-dimensional space at vertex $(1,\alpha_i)$.
  Write $\cA_i$ for the quiver obtained from the one above by erasing the arrow $\alpha_i$ and the corresponding sink.

  The representation $\tilde P_3$ is given by the quiver
  \begin{equation}
    \label{dia:P3 quiver}
    \xymatrix@R40pt@C10pt{&n-1&\\ \alpha_1^{-1}.\cA_1\ar^{\alpha_1}[ru]&\cdots&\alpha_n^{-1}.\cA_n\ar_{\alpha_n}[lu]}
  \end{equation}
  where the top vertex of dimension $n-1$ is $(1,e)$ and the arrow from $\alpha_i^{-1}.\cA_i$ emanates from its unique source~$(2,\alpha_i^{-1})$.
  Then $\tilde P_{2,i}\subset\tilde P_3$ has one-dimensional spaces at each vertex of the quiver
  \[\xymatrix@R40pt@C10pt{&&&(1,e)&&&\\ &&&(2,\alpha_i^{-1})\ar_{\alpha_i}[u]\ar_{\alpha_1}[llld]\ar_(.65){\alpha_{i-1}}[ld]\ar^(.65){\alpha_{i+1}}[rd]\ar^{\alpha_n}[rrrd]&&&\\ (1,\alpha_i^{-1}\alpha_1)&\cdots&(1,\alpha_i^{-1}\alpha_{i-1})&&(1,\alpha_i^{-1}\alpha_{i+1})&\cdots&(1,\alpha_i^{-1}\alpha_n)}\]

  The representation $\tilde P_4$ has support quiver
  \begin{equation}
    \label{dia:P4 quiver}
    \xymatrix@R40pt@C10pt{&n-1\ar_{\alpha_1}[ld]\ar^{\alpha_n}[rd]&\\ \alpha_1.\cB_1&\cdots&\alpha_n.\cB_n}
  \end{equation}
  where the top vertex of dimension $n-1$ is $(2,e)$ and $\cB_i$ is the following analogue of the support quiver for $\tilde P_3$:
  \[\xymatrix@R40pt@C10pt{&&&2n-3&&&\\
    \alpha_1^{-1}.\cA_1\ar^{\alpha_1}[rrru]&\cdots&\alpha_{i-1}^{-1}.\cA_{i-1}\ar^(.35){\alpha_{i-1}}[ru]&\widehat{\alpha_i^{-1}.\cA_i}&\alpha_{i+1}^{-1}\cA_{i+1}\ar_(.35){\alpha_{i+1}}[lu]&\cdots&\alpha_n^{-1}\cA_n\ar_{\alpha_n}[lllu]}\]
  with top vertex $(1,e)$ having dimension $2n-3$.
  Now $\tilde P_{3,i}$ can be found as the representation corresponding to the subquiver
  \[\xymatrix@R40pt@C10pt{
    &&&1\ar_{\alpha_1}[llld]\ar_(.65){\alpha_{i-1}}[ld]\ar^{\alpha_i}[d]\ar^(.65){\alpha_{i+1}}[rd]\ar^{\alpha_n}[rrrd]&&&\\
    1&\hdots&1&n-1&1&\hdots&1\\
    \alpha_i\alpha_1^{-1}.\cA_1\ar^{\alpha_1}[rrru]&\cdots&\alpha_i\alpha_{i-1}^{-1}.\cA_{i-1}\ar^(.35){\alpha_{i-1}}[ru]&&\alpha_i\alpha_{i+1}^{-1}.\cA_{i+1}\ar_(.35){\alpha_{i+1}}[lu]&\cdots&\alpha_i\alpha_n^{-1}.\cA_n\ar_{\alpha_n}[lllu]}\]
  where the top vertex is $(2,e)$ and the central vertex is $(1,\alpha_i)$.
\end{example}

The next result establishes some basic homological properties of the translated preprojective representations.
\begin{lemma}
  \label{le:homdecomposition}
  For $m\geq 1$, the following hold.
  \begin{enumerate}
    \item We have $\Hom(P_m,P_{m+1})\cong\bigoplus\limits_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
    \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
    \item For $j\in\{1,\ldots,n\}$, we have
      \[\Hom(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m,j},\tilde P_{m+1})=0.\]
    \item For each proper subset $I\subsetneq\{1,\ldots,n\}$, there exists a truncated preprojective representation~$\tilde P_{m+1}^I$ fitting into an exact sequence 
      \begin{equation}
        \label{ses1}
        \ses{\bigoplus_{i\in I} \tilde P_{m,i}}{\tilde P_{m+1}}{\tilde P_{m+1}^I}.
      \end{equation}
      Moreover, $G(\tilde P_{m+1}^I)$ is a truncated preprojective of $K(n)$ for each $I\subsetneq\{1,\ldots,n\}$.
  \end{enumerate}
\end{lemma}
\begin{remark}
  Note that when $I=\varnothing$, it follows from the definition that $\tilde P_{m+1}^I=\tilde P_{m+1}$.
\end{remark}
\begin{proof}
  Part (1) is immediate from Theorem~\ref{covering}.
  Part (2) is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq j\leq n$, we have 
  $$\CC\cong\Hom(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m,j}).$$
  But $\Hom(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.

@@

  For part (4), observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to the subspace $V\subset H_m$ spanned by the generators of the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
  The map $\bigoplus_{i\in I} \tilde P_{m,i}\to\tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^I$ and the preceding discussion shows that $G(\tilde P_{m+1}^I)\cong P_{m+1}^V$ is truncated preprojective as well.
\end{proof}

In what follows, we will need to understand the homological properties of the truncated preprojectives for $\widetilde{K(n)}$.
\begin{lemma}
  \label{le:properties}
  For $m\geq1$ and $I\subsetneq\{1,\ldots,n\}$, the following hold.
  \begin{enumerate}
    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\ne0$ if and only if $j\notin I$, in which case 
      \[\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Hom(\tilde P_{m,j},\tilde P_{m+1})\cong\CC.\] 
    \item We have $\Hom(\tilde P_{m+1},\tilde P_{m+1}^I)\cong\CC$ and $\Ext(\tilde P_{m+1},\tilde P_{m+1}^I)=0$. 
    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$.
      Also, $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ne0$ if and only if $j\in I$, in which case  
      \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC.\] 
    \item We have $\Hom(\tilde P_{m+1}^I,\tilde P_{m+1}^I)\cong\CC$ and $\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0$.
      In particular, $\tilde P_{m+1}^I$ is an exceptional representation of $\widetilde{K(n)}$.
    %\item We have $\Hom(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=0$ and $\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\CC$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  Applying $\Hom(\tilde P_{m,j},-)$ to the sequence \eqref{ses1} gives the exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(\tilde P_{m,j},\bigoplus_{i\in I} \tilde P_{m,i}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}^I) \ar[r] & 0},\]
  where the final zero follows from Lemma~\ref{le:homdecomposition}.(2).
  Now the middle space is one-dimensional while the left-hand space vanishes if and only if $j\notin I$, this proves part (1).

@@

\begin{example}
  \label{ex:truncated lifts}
  Fix $I\subsetneq\{1,\ldots,n\}$.
  Building on Example~\ref{ex:lifted preprojectives}, we describe here the truncated preprojectives $\tilde P_m^I$ for $m=2,3,4$.
  Following Lemma~\ref{le:properties}.(4), we can do this by simply specifying their dimension vectors as we did above.

  The support quiver of $\tilde P_2^I$ is obtained from the quiver \eqref{dia:P2 quiver} of $\tilde P_2$ by removing the sinks $(1,\alpha_i)$ for $i\in I$.
  The support quiver of $\tilde P_3^I$ is obtained from the quiver \eqref{dia:P3 quiver} of $\tilde P_3$ by removing the subquivers $\alpha_i^{-1}.\cA_i$ for $i\in I$ and decreasing the dimension of the space at vertex $(1,e)$ by $|I|$.

  The support quiver of $\tilde P_4^I$ is given by the following analogue of the quiver \eqref{dia:P4 quiver} of $\tilde P_4$:
  \[\xymatrix@R40pt@C10pt{&n-1-|I|\ar_{\alpha_1}[ld]\ar^{\alpha_n}[rd]&\\ \alpha_1.\cB_1^I&\cdots&\alpha_n.\cB_n^I}\]
  where the top vertex of dimension $n-1-|I|$ is again $(2,e)$ and $\cB_i^I$ is simply a space of dimension~$n-1-|I|$ if $i\in I$ and otherwise is the quiver
  \[\xymatrix@R40pt@C10pt{&&&2n-3-|I|&&&\\
    \alpha_1^{-1}.\cA_1\ar^{\alpha_1}[rrru]&\cdots&\alpha_{i-1}^{-1}.\cA_{i-1}\ar^(.35){\alpha_{i-1}}[ru]&\widehat{\alpha_i^{-1}.\cA_i}&\alpha_{i+1}^{-1}\cA_{i+1}\ar_(.35){\alpha_{i+1}}[lu]&\cdots&\alpha_n^{-1}\cA_n\ar_{\alpha_n}[lllu]}\]
\end{example}

\begin{lemma}
  \label{le:truncated tau}
  For $m\ge3$ and $I\subsetneq\{1,\ldots,n\}$, we have $\tilde\Sigma_2(\tilde P_{m-1}^I)^\sigma=\tilde P_m^I$ and $\tau\tilde P_{m+1}^I=\tilde P_{m-1}^I$.
\end{lemma}
\begin{proof}
  By Lemma~\ref{le:homdecomposition}, we get the short exact sequence \eqref{ses1} defining the truncated preprojective $\tilde P_{m-1}^I$:
  \[\ses{\bigoplus_{i\in I} \tilde P_{m-2,i}}{\tilde P_{m-1}}{\tilde P_{m-1}^I}.\]
  Applying the functor $\tilde\Sigma_2(-)^\sigma$ to this sequence and recalling the reflection recursion \eqref{eq:recursive covers}, we obtain a short exact sequence
  \[\ses{\bigoplus_{i\in I} \tilde P_{m-1,i}}{\tilde P_m}{\tilde\Sigma_2(\tilde P_{m-1}^I)^\sigma}.\]
  The equality $\tilde\Sigma_2(\tilde P_{m-1}^I)^\sigma=\tilde P_m^I$ immediately follows.
  The equality $\tilde P_{m+1}^I=\tau^{-1}\tilde P_{m-1}^I$ is obtained in the same way using the functor $\tilde\Sigma_1\tilde\Sigma_2=\tau^{-1}$.
\end{proof}

Now we introduce notation for locating lifted preprojectives as subrepresentations of other lifted preprojective representations.
Since we work only on two fixed components of $\widetilde{K(n)}$, the following notation will be useful in describing paths in these components.
For $l\ge1$, set
\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\}\text{ for $1\le j\le l$}\}.\]%, i_j\ne i_{j+1}\text{ for $1\le j<l$}\}.\]
Depending on context (in particular, the parity of $m+1$ below), we will sometimes identify the word~$(i_1,\ldots,i_l)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_l}^{(-1)^{l+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_l}^{(-1)^l}\in W_n$.
In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$, we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
More precisely, we obtain a sequence of preprojective representations which uniquely determines the desired inclusion:
\[\tilde P_{m+1-k,\ui}\subset \tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-1,(i_1,i_2)}\subset \tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
